% ================================
% Mehmet Yigit Turali — One-Page, Two-Column Research Resume
% Apple AI/ML Research–oriented • balanced columns • single page
% ================================
\documentclass[letterpaper,10pt]{article}

% --- Core look & spacing ---
\usepackage[margin=0.6in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome5}
\usepackage{microtype}
\usepackage{url}
\usepackage{ragged2e}
\usepackage{setspace}
\usepackage{array}
\usepackage{ifthen}
\usepackage{tabularx}                 % <-- added for inline headers
\usepackage[sfdefault]{sourcesanspro} % clean, readable sans serif

\urlstyle{same}
\microtypecontext{spacing=nonfrench}
\setstretch{0.98}                 % subtle vertical compression
\setlength{\parskip}{0pt}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*, itemsep=2pt, topsep=2pt, parsep=0pt}
\setlist[enumerate]{leftmargin=*, itemsep=2pt, topsep=2pt, parsep=0pt}

% --- Section style ---
\titleformat{\section}
  {\large\bfseries\scshape}
  {}{0pt}{}[\vspace{-2pt}\titlerule]
\titlespacing*{\section}{0pt}{4pt}{3pt}

% --- Small helpers ---
\newcommand{\dotsep}{\hspace{0.35em}\textbar\hspace{0.35em}} % robust separator
\newcommand{\role}[1]{\emph{#1}}
\newcommand{\daterange}[1]{\textbf{\small #1}}

% --- Inline header: Name — Location  |  Dates (right aligned)
\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}p{0.28\linewidth}} % tweak width as needed
\newcommand{\entryinline}[3]{%
  \begin{tabularx}{\linewidth}{@{}L R@{}}%
    \textbf{#1} \textit{— #2} & \small #3\\
  \end{tabularx}%
}

% --- Header ---
\begin{document}
\begin{center}
  {\Large \scshape Mehmet Yigit Turali}\\[-1pt]
  Department of Electrical \& Computer Engineering, UCLA\\[-1pt]
  \href{mailto:myigitturali@ucla.edu}{\faEnvelope\ myigitturali@ucla.edu}
  \dotsep \href{https://yigitturali.com}{\faGlobeAmericas\ yigitturali.com}
  \dotsep \href{https://github.com/YigitTurali}{\faGithub\ github.com/YigitTurali}
\end{center}
\vspace{-2pt}

% ================================
% Two columns using minipages (predictable & balanced)
% Widened gutter for breathing room
% ================================
\begin{minipage}[t]{0.60\textwidth}

\section{Education}
\entryinline{University of California, Los Angeles (UCLA)}{Los Angeles, CA}{Sep 2024 — Present}
Ph.D. in Electrical \& Computer Engineering, GPA: 3.94/4.00 \\
Advisor: Dr. Vwani P. Roychowdhury

\medskip
\entryinline{Bilkent University}{Ankara, Turkey}{Sep 2019 — Jun 2024}
B.S. in Electrical \& Electronics Engineering, GPA: 3.83/4.00 \\
\emph{Summa Cum Laude}

\section{Research \& Professional Experience}

\entryinline{Generative Semantic Workspace (GSW) — UCLA}{Los Angeles, CA}{Jun 2024 — Present}
\role{Graduate Student Researcher}
\begin{itemize}
  \item Research large language model reasoning and retrieval under Prof. Vwani P. Roychowdhury.
\item Develop a reranker-scored, beam-style multi-hop retrieval pipeline that expands and selects top-$k$ contexts for consistent reasoning.
  \item Construct structured semantic graphs and custom vector-database interfaces (FAISS, Pinecone) for dynamic memory updates and context tracking across reasoning steps.
\end{itemize}

\entryinline{LLM-Based Genomic Variant Detection — UCLA}{Los Angeles, CA}{Sep 2024 — Present}
\role{Graduate Student Researcher}
\begin{itemize}
  \item Develop transformer one-shot models that treat DNA as language for reference-free variant detection.
  \item Introduce contrastive DNA embeddings for semantically meaningful genomic representations.
\end{itemize}

\entryinline{Brain Organoid Computing — UCLA}{Los Angeles, CA}{Sep 2024 — Present}
\role{Graduate Student Researcher}
\begin{itemize}
  \item Explore organoid-based reservoir computing for forecasting chaotic time series.
  \item Implement electrode-array interfacing \& stimulation pipelines to optimize nonlinear prediction.
\end{itemize}

\entryinline{Prior Research (Bilkent University)}{Ankara, TR}{2021 — 2024}
\role{Undergraduate Researcher}
\begin{itemize}
  \item Developed gradient boosting with moving-average terms for sequential regression (\emph{IEEE SPL 2023}).
  \item Designed adaptive feature selection via binary masking (\emph{Neural Computing \& Applications 2025}).
\end{itemize}

\entryinline{DataBoss Security \& Analytics}{Ankara, TR}{2022 — 2024}
\role{Machine Learning Researcher}
\begin{itemize}
  \item Built AI agents and RAG chatbots with LangChain; designed self-multi RAG and retrieval-rank pipelines.
  \item Created GBM variants with moving-average terms for renewable energy and finance forecasting.
\end{itemize}

\entryinline{National Magnetic Resonance Research Center (UMRAM)}{Bilkent Univ.}{2021 — 2022}
\role{Computer Vision Researcher}
\begin{itemize}
  \item CNNs for sacroiliitis detection (JointNET) from X-ray images.
  \item Multi-branch transformer (HydraViT) for thoracic disease multi-label classification.
\end{itemize}

\end{minipage}
\hspace{0.06\textwidth} % wider gutter between columns
\begin{minipage}[t]{0.34\textwidth}

\section{Publications}
\small
\begin{itemize}[leftmargin=0in, itemsep=1pt]
  \item Z. Fei$^{*}$, \textbf{M. Y. Turali}$^{*}$, et al., \href{https://neurips.cc/}{\emph{Customizing Open-Source LLMs for Quantitative Medication Attribute Extraction across Heterogeneous EHR Systems}}, NeurIPS 2025 Workshop on GenAI for Health. {\footnotesize $^{*}$Equal contribution.}
  \item \textbf{M. Y. Turali}, M.E. Lorasdagi, S.S. Kozat, \href{https://doi.org/10.1007/s00521-024-10913-9}{\emph{Binary Feature Mask Optimization for Feature Selection}}, Neural Computing \& Applications, 2025.
  \item \textbf{M. Y. Turali}, A.T. Koc, S.S. Kozat, \href{https://doi.org/10.1016/j.dsp.2024.104731}{\emph{Optimal Stochastic Gradient Descent Algorithm for Filtering}}, Digital Signal Processing, 2024.
  \item \textbf{M. Y. Turali}, M.E. Lorasdagi, S.S. Kozat, \href{https://doi.org/10.1007/s11760-024-03411-x}{\emph{AFS-BM: Enhancing Model Performance through Adaptive Feature Selection with Binary Masking}}, Signal, Image and Video Processing (SIViP), 2024.
  \item E. Ilhan, \textbf{M. Y. Turali}, S.S. Kozat, \href{https://doi.org/10.1109/LSP.2023.3309577}{\emph{Gradient Boosting With Moving-Average Terms for Nonlinear Sequential Regression}}, IEEE Signal Processing Letters, 2023.
  \item Ş. Öztürk, \textbf{M. Y. Turalı}, T. Çukur, \href{https://doi.org/10.1016/j.bspc.2024.106959}{\emph{HydraViT: Adaptive Multi-Branch Transformer for Multi-Label Disease Classification from Chest X-ray Images}}, Biomedical Signal Processing and Control, 2025.
  \item S. Turk, A. Demirkaya, \textbf{M. Y. Turali}, \href{https://doi.org/10.48550/arXiv.2301.10769}{\emph{JointNET: A Deep Model for Predicting Active Sacroiliitis from Sacroiliac Joint Radiography}}, arXiv:2301.10769, 2023.
\end{itemize}
\normalsize

\section{Honors \& Awards}
\begin{itemize}
  \item \textbf{Bilkent University Research Excellence Award} (2024)
  \item \textbf{Responsible AI Innovation Award} — MathWorks \& FIGES (2024)
  \item \textbf{Shell Cashflow Forecasting Datathon} — 4th Place (2023)
  \item \textbf{Bilkent University Comprehensive Scholarship} (2019–2024)
\end{itemize}

\section{Technical Skills}
\begin{itemize}
  \item \textbf{Programming:} Python, MATLAB, Verilog HDL
  \item \textbf{Frameworks:} PyTorch, TensorFlow, Keras, Transformers, Hugging Face
  \item \textbf{Vector Databases:} FAISS, Pinecone, LangChain
  \item \textbf{ML Tools:} scikit-learn, Pandas, NumPy, Matplotlib
  \item \textbf{Neuro/Signal:} Elephant, Kilosort, SpikeInterface
  \item \textbf{Dev Tools:} Docker, Git, \LaTeX
\end{itemize}

\end{minipage}
\end{document}